---
title: "Pizza Party"
author: "Charles Zhang, Jinghan Zhou, Roan Floer-Martinez,Xi Feng"
output: 
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

```{r message=FALSE}
library(sf) 
library(leaflet)
library(RColorBrewer)
library(plotly)
library(tidyverse)
library(lubridate)
library(skimr) 
library(shiny)
library(readr)
library(gplots) 
library(ggmap)
library(naniar) 
library(formattable)
```

```{r}
# Read Data
pizza_datafiniti <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_datafiniti.csv") %>% 
  unique()
pizza_jared <- readr::read_csv("https://raw.githubusercontent.com/RoanFM/Compsci-final/master/Data/pizza_jared.csv") %>% 
  unique() 
pizza_barstool <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_barstool.csv") %>% 
  unique()
```

## **Introduction**

#### Our goal is to help people find the best pizza in New York, depending on their location in the city, price range, and kind of pizzeria they are looking for. To do this, we used three datasets from the TidyTuesday Pizza Party set. We used a dataset from DataFiniti which provides use with geographic data of over 10000 pizza places. 

```{r}
leaflet(data=pizza_datafiniti) %>% 
  addProviderTiles(providers$Esri.NatGeoWorldMap) %>% 
  addCircleMarkers(lng = ~longitude, lat = ~latitude, color = "red", label=~name,stroke = FALSE, fillOpacity = 0.5, radius = 2.2)
```

#### As this dataset shows that New York city has the most pizza(not include Brokklyn), using pizzateria places in New York City in our research will be meaningful and representative.

```{r}
pizza_datafiniti %>% 
  group_by(city) %>% 
  summarise(n = n()) %>%
  mutate(city = fct_reorder(city, n)) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  ggplot(aes(x=city, y=n,fill=city))+
  geom_col()+
  coord_flip()+
  theme_minimal()+
  theme(legend.position="none")+
  ylab("Number of Pizza Places")+
  labs(title = "Top 10 Cities for Pizza")
```

#### We then crossed this against two datasets which included ratings, one by Jared Lander which has ratings from New York locals, and one from the Barstool Sports magazines which covers pizzerias across the nation but only has ratings from Barstool employees. 

#### Next, we compared the average review socres among NYC, Brooklyn, Boston, and Minneapolis, places that are known for pizza in the Barstool's dataset. 

```{r, results='hide'}
pizza_barstool %>% 
  filter(city == c("New York", "Brooklyn", "Chicago", "Boston")) %>% 
  ggplot(aes(x=review_stats_all_average_score))+
  geom_histogram(aes(fill = city))+
  theme_minimal()+
  facet_wrap(~city)+
  theme(legend.position="none")+
  labs(title = "Average Rating Scores")+
  xlim(0,10)+
  xlab("Average Review Rating Score")
```

#### This plot implies that we have more significant distrubution for the average rating socre in New York. This is also the reason why we choose to use pizzeria in NYC. 


### **Analysis**

#### We have different methods for pizza ratings, so we would like to analyze the differences similarities between each mathed first. 

```{r, results='hide'}
pizza_barstool %>% 
  mutate(community = review_stats_community_average_score, all = review_stats_all_average_score, dave = review_stats_dave_average_score) %>% 
  select(name, all, community, dave) %>% 
  pivot_longer(cols = -name, names_to = "category", values_to = "score") %>% 
  ggplot(aes(x=score))+
  geom_histogram(aes(fill=category), alpha = 0.4)+
  geom_density(aes(y=..density..*count, color = category), position='dodge', alpha = 0, size= 1)+
  theme_minimal()+
  facet_wrap(~category)+
  theme(legend.position="none")+
  labs(title = "Average Rating Scores")
```

#### Overall, the average scores distributions of all reviews, the community rating, and the Dave rating are similar but still exist differences.

#### **Our Rating Method**

```{r, results='hide'}
glimpse(pizza_jared)
pizza_jared<-pizza_jared %>% 
  mutate(date = as_datetime(time)) 
glimpse(pizza_jared)
```

```{r, results='hide'}
# sum the total votes and rate
pizza_excellent <- pizza_jared %>% 
  filter(answer=="Excellent") %>% 
  group_by(place) %>% 
  mutate(sum_votes=sum(votes), sum_total=sum(total_votes)) %>% 
  mutate(p = sum_votes/sum_total)

pizza_good <- pizza_jared %>% 
  filter(answer=="Good") %>% 
  group_by(place) %>% 
  mutate(sum_votes=sum(votes), sum_total=sum(total_votes)) %>% 
  mutate(p = sum_votes/sum_total)

pizza_average <- pizza_jared %>% 
  filter(answer=="Average") %>% 
  group_by(place) %>% 
  mutate(sum_votes=sum(votes), sum_total=sum(total_votes)) %>% 
  mutate(p = sum_votes/sum_total)

pizza_poor <- pizza_jared %>% 
  filter(answer=="Poor") %>% 
  group_by(place) %>% 
  mutate(sum_votes=sum(votes), sum_total=sum(total_votes)) %>% 
  mutate(p = sum_votes/sum_total)

pizza_never <- pizza_jared %>% 
  filter(answer=="Never Again") %>% 
  group_by(place) %>% 
  mutate(sum_votes=sum(votes), sum_total=sum(total_votes)) %>% 
  mutate(p = sum_votes/sum_total)

# create pizza rating data frame
pizza_rating <- rbind(pizza_excellent, pizza_good, pizza_average, pizza_poor, pizza_never) %>% 
  mutate(year=year(date)) %>% 
  group_by(place, year, answer) %>% 
  mutate(year_avr_rate = mean(p)) 

glimpse(pizza_rating)
```
```{r, results='hide'}
# Top ten highest Excerllent rate 
top_ten_excellent<-pizza_rating %>% 
  filter(answer=="Excellent") %>% 
  group_by(place) %>% 
  summarise(eExcellent = sum(year_avr_rate)/n()) %>% 
  arrange(desc(eExcellent)) %>% 
  head(10) 

# Other answers for these ten pizzas
top_exe_good <- top_ten_excellent %>% 
  inner_join(pizza_rating, by="place") %>% 
  filter(answer=="Good") %>% 
  group_by(place) %>% 
  summarise(dGood = sum(year_avr_rate)/n()) 

top_exe_avr<- top_ten_excellent %>% 
  inner_join(pizza_rating, by="place") %>% 
  filter(answer=="Average") %>% 
  group_by(place) %>% 
  summarise(cAverage = sum(year_avr_rate)/n()) 

top_exe_poor<- top_ten_excellent %>% 
  inner_join(pizza_rating, by="place") %>% 
  filter(answer=="Poor") %>% 
  group_by(place) %>% 
  summarise(bPoor = sum(year_avr_rate)/n()) 

top_exe_never<- top_ten_excellent %>% 
  inner_join(pizza_rating, by="place") %>% 
  filter(answer=="Never Again") %>% 
  group_by(place) %>% 
  summarise(aNever_Again = sum(year_avr_rate)/n())

top_ten_excellent_analysis <- top_ten_excellent %>% 
  inner_join(top_exe_good,by = "place") %>% 
  inner_join(top_exe_avr,by = "place") %>% 
  inner_join(top_exe_poor,by = "place") %>% 
  inner_join(top_exe_never,by = "place") %>% 
  pivot_longer(cols= -place,names_to = "Answers",values_to = "Proportion") 

```

#### Our data came with ratings for various pizza places. We wanted to find the best pizza places in New York based off this. However, we didn't just want to calculate the average rating because we think an extreme rating can be more telling. As a result, we calculated the proportion of all ratings among the overall reviews and sorted by the highest proportion of reviews rating the pizzerias as "excellent". Of those ten, only Little Italy Pizza had reviewers who said they would never go back and four had no "poor" ratings either. Patsy's pizza (which I used to order as a kid!) was the winner with 2/3rds of reviewers calling its pizza "excellent". 

```{r, fig.width=8}
# Graph
top_ten_excellent_analysis %>% 
  ggplot(aes(x=place, y=Proportion, fill=Answers))+
  geom_bar(stat='identity')+
  scale_fill_manual("legend", values = c("red","salmon","pink","steelblue1","steelblue4"), label = c("Never Again","Poor","Average","Good","Excellent"))+
  theme_classic()+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  xlab("Place")+
  labs(title = "Evaluation for Top 10 Pizza Place in NYC")+
  guides(fill=guide_legend(NULL))+
  scale_x_discrete(limits=c("Patsy's", "Naples 45", "Tappo", "Bleecker Street Pizza", "Little Italy Pizza", "Artichoke Basille's Pizza", "Spunto", "Gotham Pizza", "5 Boroughs Pizza", "Pizza Bash"))
  
```








