---
title: "Pizza Party"
author: "Charles Zhang, Jinghan Zhou, Roan Floer-Martinez,Xi Feng"
output: 
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

```{r message=FALSE}
library(sf) 
library(leaflet)
library(RColorBrewer)
library(plotly)
library(tidyverse)
library(lubridate)
library(gplots) 
library(ggmap)
library(naniar) 
library(formattable)
library(skimr) 
library(shiny)
library(readr)
```

```{r}
# Read Data
pizza_datafiniti <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_datafiniti.csv") %>% 
  unique()
pizza_jared <- readr::read_csv("https://raw.githubusercontent.com/RoanFM/Compsci-final/master/Data/pizza_jared.csv") %>% 
  unique() 
pizza_barstool <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_barstool.csv") %>% 
  unique()
```


### Introduction
#### It seems like everyone has a favorite pizzeria. Whether it’s the one that delivers until 2 AM, the one with the best sauce, or the really cheap one down the block, it’s very hard to find a pizzeria that everyone will like. 
#### Using some data from TidyTuesday’s Pizza Party dataset, we tried to solve this problem. It contains three datasets, one from DataFiniti which has more than 10,000 pizza places from across the country; one from the Barstool Sports magazine which has price categories, locations, and reviews from Barstool critics and community members; and a dataset from Jared Lander, who surveyed people on New York Pizzerias and asked people to rate them on a six point like scale. We have used all three datasets, and it’s given us a pretty good sense of the best pizza in New York. 
#### We started out by mapping the DataFiniti dataset. Obviously it doesn’t include every single pizzeria in the country, and it doesn’t have franchises like Domino’s. However, it shows fairly well where pizza places are concentrated in this country. 


```{r}
leaflet(data=pizza_datafiniti) %>% 
  addProviderTiles(providers$Esri.NatGeoWorldMap) %>% 
  addCircleMarkers(lng = ~longitude, lat = ~latitude, color = "red", label=~name,stroke = FALSE, fillOpacity = 0.5, radius = 2.2)
```

#### Since there is so much regional pride in pizza, and to get a better sense of where pizzerias are concentrated, we then sorted and graphed our cities by the number of pizza places. It’s important to note that, in this dataset, the different boroughs of New York City are considered to be different cities. Regardless, Manhattan has by far the most pizzerias, with nearly 100. Brooklyn comes in second with just over 50, and Chicago and Philadelphia have about 30 each. 

```{r}
pizza_datafiniti %>% 
  group_by(city) %>% 
  summarise(n = n()) %>%
  mutate(city = fct_reorder(city, n)) %>% 
  arrange(desc(n)) %>% 
  head(10) %>% 
  ggplot(aes(x=city, y=n,fill=city))+
  geom_col()+
  coord_flip()+
  theme_minimal()+
  theme(legend.position="none")+
  ylab("Number of Pizza Places")+
  labs(title = "Top 10 Cities for Pizza")
```

####	We then looked at four of the top cities for pizza in the country, Boston, Brooklyn, Chicago, and New York. We compared the average ratings for pizzerias. Most of the cities’ averages were around 6 or 7, except Chicago. I guess not even Chicagoans like Deep Dish! As was expected, New York had by far the most pizzerias. 

```{r, results='hide'}
pizza_barstool %>% 
  filter(city == c("New York", "Brooklyn", "Chicago", "Boston")) %>% 
  ggplot(aes(x=review_stats_all_average_score))+
  geom_histogram(aes(fill = city))+
  theme_minimal()+
  facet_wrap(~city)+
  theme(legend.position="none")+
  labs(title = "Average Rating Scores")+
  xlim(0,10)+
  xlab("Average Review Rating Score")
```

#### Since we have three different rating systems, we wondered if it’s even possible to get a reliable conclusion from them. To check this, we compared the distribution of ratings across the different datasets. All three had an average of roughly 7.5 and very similar bell curve patterns, which shows that there was at least some consistency in the rating scales. 

```{r, results='hide'}
pizza_barstool %>% 
  mutate(community = review_stats_community_average_score, all = review_stats_all_average_score, dave = review_stats_dave_average_score) %>% 
  select(name, all, community, dave) %>% 
  pivot_longer(cols = -name, names_to = "category", values_to = "score") %>% 
  ggplot(aes(x=score))+
  geom_histogram(aes(fill=category), alpha = 0.4)+
  geom_density(aes(y=..density..*count, color = category), position='dodge', alpha = 0, size= 1)+
  theme_minimal()+
  facet_wrap(~category)+
  theme(legend.position="none")+
  labs(title = "Average Rating Scores")
```

#### With that in mind, we tried to find the best pizza in New York. First, we compared Dave’s ratings with the community average across the whole dataset. 
Then, we looked at Jared’s data to try and find the community’s choice for the best pizza. We think that an extreme response is more meaningful than a simple average of the ratings, so we calculated the proportion of customers who rated the pizza as excellent. The top ten highest proportions ranked as excellent are graphed here.


```{r}
a<-pizza_barstool %>% 
  #mutate(top_ten = ifelse(name %in% pizza_names, "yes", "no")) %>% 
  filter(review_stats_dave_average_score!=0, review_stats_community_average_score!=0) %>% 
  ggplot(aes(x=review_stats_dave_average_score, y = review_stats_community_average_score, label=name))+
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)+
  theme_minimal()

ggplotly(a)
```


```{r, results='hide'}
glimpse(pizza_jared)
pizza_jared<-pizza_jared %>% 
  mutate(date = as_datetime(time)) 
glimpse(pizza_jared)
```

```{r, results='hide'}
# sum the total votes and rate
pizza_excellent <- pizza_jared %>% 
  filter(answer=="Excellent") %>% 
  group_by(place) %>% 
  mutate(sum_votes=sum(votes), sum_total=sum(total_votes)) %>% 
  mutate(p = sum_votes/sum_total)

pizza_good <- pizza_jared %>% 
  filter(answer=="Good") %>% 
  group_by(place) %>% 
  mutate(sum_votes=sum(votes), sum_total=sum(total_votes)) %>% 
  mutate(p = sum_votes/sum_total)

pizza_average <- pizza_jared %>% 
  filter(answer=="Average") %>% 
  group_by(place) %>% 
  mutate(sum_votes=sum(votes), sum_total=sum(total_votes)) %>% 
  mutate(p = sum_votes/sum_total)

pizza_poor <- pizza_jared %>% 
  filter(answer=="Poor") %>% 
  group_by(place) %>% 
  mutate(sum_votes=sum(votes), sum_total=sum(total_votes)) %>% 
  mutate(p = sum_votes/sum_total)

pizza_never <- pizza_jared %>% 
  filter(answer=="Never Again") %>% 
  group_by(place) %>% 
  mutate(sum_votes=sum(votes), sum_total=sum(total_votes)) %>% 
  mutate(p = sum_votes/sum_total)

# create pizza rating data frame
pizza_rating <- rbind(pizza_excellent, pizza_good, pizza_average, pizza_poor, pizza_never) %>% 
  mutate(year=year(date)) %>% 
  group_by(place, year, answer) %>% 
  mutate(year_avr_rate = mean(p)) 

glimpse(pizza_rating)
```
```{r, results='hide'}
# Top ten highest Excerllent rate 
top_ten_excellent<-pizza_rating %>% 
  filter(answer=="Excellent") %>% 
  group_by(place) %>% 
  summarise(eExcellent = sum(year_avr_rate)/n()) %>% 
  arrange(desc(eExcellent)) %>% 
  head(10) 

# Other answers for these ten pizzas
top_exe_good <- top_ten_excellent %>% 
  inner_join(pizza_rating, by="place") %>% 
  filter(answer=="Good") %>% 
  group_by(place) %>% 
  summarise(dGood = sum(year_avr_rate)/n()) 

top_exe_avr<- top_ten_excellent %>% 
  inner_join(pizza_rating, by="place") %>% 
  filter(answer=="Average") %>% 
  group_by(place) %>% 
  summarise(cAverage = sum(year_avr_rate)/n()) 

top_exe_poor<- top_ten_excellent %>% 
  inner_join(pizza_rating, by="place") %>% 
  filter(answer=="Poor") %>% 
  group_by(place) %>% 
  summarise(bPoor = sum(year_avr_rate)/n()) 

top_exe_never<- top_ten_excellent %>% 
  inner_join(pizza_rating, by="place") %>% 
  filter(answer=="Never Again") %>% 
  group_by(place) %>% 
  summarise(aNever_Again = sum(year_avr_rate)/n())

top_ten_excellent_analysis <- top_ten_excellent %>% 
  inner_join(top_exe_good,by = "place") %>% 
  inner_join(top_exe_avr,by = "place") %>% 
  inner_join(top_exe_poor,by = "place") %>% 
  inner_join(top_exe_never,by = "place") %>% 
  pivot_longer(cols= -place,names_to = "Answers",values_to = "Proportion") 

```

#### Our data came with ratings for various pizza places. We wanted to find the best pizza places in New York based off this. However, we didn't just want to calculate the average rating because we think an extreme rating can be more telling. As a result, we calculated the proportion of all ratings among the overall reviews and sorted by the highest proportion of reviews rating the pizzerias as "excellent". Of those ten, only Little Italy Pizza had reviewers who said they would never go back and four had no "poor" ratings either. Patsy's pizza (which I used to order as a kid!) was the winner with 2/3rds of reviewers calling its pizza "excellent". 

```{r, fig.width=8}
# Graph
top_ten_excellent_analysis %>% 
  ggplot(aes(x=place, y=Proportion, fill=Answers))+
  geom_bar(stat='identity')+
  scale_fill_manual("legend", values = c("red","salmon","pink","steelblue1","steelblue4"), label = c("Never Again","Poor","Average","Good","Excellent"))+
  theme_classic()+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  xlab("Place")+
  labs(title = "Evaluation for Top 10 Pizza Place in NYC")+
  guides(fill=guide_legend(NULL))+
  scale_x_discrete(limits=c("Patsy's", "Naples 45", "Tappo", "Bleecker Street Pizza", "Little Italy Pizza", "Artichoke Basille's Pizza", "Spunto", "Gotham Pizza", "5 Boroughs Pizza", "Pizza Bash"))
  
```

#### Then, we combined the final two graphs, which gives us, we think, a good sense of the best pizza in the country. 

```{r}
pizza_names <-
  top_ten_excellent %>% 
  pull(place)
```
```{r}
b<-pizza_barstool %>% 
  mutate(top_ten = ifelse(name %in% pizza_names, "yes", "no")) %>% 
  filter(review_stats_dave_average_score!=0, review_stats_community_average_score!=0) %>% 
  ggplot(aes(x=review_stats_dave_average_score, y = review_stats_community_average_score, label=name))+
  geom_point(aes(color=top_ten))+
  geom_smooth(method = "lm", se = FALSE)+
  theme_minimal()

ggplotly(b)

```

```{r}
pizza_barstool %>% 
  filter(review_stats_all_count>=50) %>% 
  mutate(name = fct_reorder(name, review_stats_all_average_score)) %>% 
  ggplot(aes(review_stats_all_average_score, name, size=review_stats_all_count, name)) +
  geom_point() +
  labs(x="Average rating", size="# of review", y="",
       title="Barstool Sports ratings of pizza places",
       subtitle = "only places with at least 50 reviews")+
  theme_minimal()
```



