---
title: "ideas"
author: "Charles Zhang, Roan Floer-Martinez, Jinghan Zhou, Xi Feng"
output: 
  html_document:
    keep_md: yes
---
```{r message=FALSE}
library(readr)
library(tidyverse)
library(lubridate)
library(skimr) 
library(naniar) 
library(ggmap)
library(gplots) 
library(RColorBrewer) 
library(sf) 
library(leaflet)
library(formattable)
```

## Dataset 1: Board Games

```{r message=FALSE, warning=FALSE}
board_games <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-03-12/board_games.csv")
```

## Dataset 2: Video Games
> *Data:* 
https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-07-30
This dataset seems pretty interesting and straightforward

```{r message=FALSE}
library(readr)
video_games <- read_csv("~/Desktop/Compsci-final/ideas/video_games.csv")

video_games[video_games==0] <- NA
vg_clean<-video_games %>% 
  drop_na() 
```

> **Ideas:**
find out the popularity/trend of Video games and compare the different video games companies by those variables in the data.

> **Graphs/Tables:**

```{r message=FALSE}
vg_clean %>% 
  ggplot(aes(x = price))+
  geom_density() +
  theme_classic()

top_20_avrplaytime_game <- vg_clean %>% 
  select(game, average_playtime, price, owners) %>% 
  arrange(desc(average_playtime)) %>% 
  head(20)

top_20_avrplaytime_game %>% 
  ggplot(aes(x=price, y=average_playtime,label=game, color = owners))+
  geom_point()+
  geom_text(family="STKaiti")+
  theme_classic()
```

> This graph shows the relation between pices of games, average play times of games, and the number of owners of games with top 20 average playtime


## Dataset 3: Pizza Party

> **Data:**

```{r message=FALSE}
pizza_jared <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_jared.csv")
pizza_barstool <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_barstool.csv")
pizza_datafiniti <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_datafiniti.csv")
```

> **Graphs/Tables**

> Pizza in the U.S.

```{r message=FALSE, warning=FALSE}
leaflet(data=pizza_datafiniti) %>% 
  addProviderTiles(providers$Esri.NatGeoWorldMap) %>% 
  addCircleMarkers(lng = ~longitude, lat = ~latitude, color = "red", label=~name,stroke = FALSE, fillOpacity = 0.5, radius = 2)
```

```{r message=FALSE, warning=FALSE}
mn_pizza <- pizza_datafiniti %>% 
  filter(province == "MN")
```

> Pizza in the Minnesota

```{r message=FALSE, warning=FALSE}

palmn <- colorFactor(topo.colors(5), 
                     domain = mn_pizza$price_range_max) 

leaflet(data=mn_pizza) %>% 
  addProviderTiles(providers$Stamen.Toner) %>% 
  addMarkers(lng = ~longitude, lat = ~latitude, label = ~name,clusterOptions = markerClusterOptions())

```






